Reading Notes

### 2020-08-11 2pd.tex
pre boss suggestions

\section*{Research Objectives}
<gain insight into the limits of coarse graining>
<create models for new opv compounds>
<create a workflow that will make creating new models more accessible>
<develop new tools that help humans do science>
<use that science to help solve energy crisis???????>
<I don't know where to put this but I want a section on best practices>
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
live coding, interactive \cite{Wilson2016}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}

@@

\subsection*{Organic Photovoltaics}
<what is PCE>
The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device over the power of incedent photons.
Higher PCE means the device is more efficient.  
The material properties which determine the PCE of a device are those which affect the number of photons absorbed, excitons dissociated, and free charges that reach the electrode.
The absorption efficiency depends on the absorption spectrum, absorption coefficient, and layer thickness.
The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface.
Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes.\cite{Hoppe2004}
<is there a citation for why charge transport is a good proxy for PCE?>

@@

\subsection*{Mesoscale Device Simulation}
<I DONT WANT TO FOCUS ON THIS TOO MUCH. It's only here as a rationale for why backmapping>
<how morphct pipeline would work: cg-backmap-ct>
MorphCT, a software previously developed by our lab, can simulate charge transport through an OPV morphology using kinetic Monte Carlo\cite{Miller2018a,MorphCT,morphct2.2}.
The kinetic Monte Carlo algorithm used by MorphCT uses the semi-empirical Zerner's Intermediate Neglect of Differential Overlap (ZINDO/S) quantum chemical calculation to obtain the molecular energy levels of chromophores in the morphology.
The HOMO levels of each chromophore site and the energy splitting induced in the chromophore pairs is used in the Marcus equation to calculate the charge hopping rate between pairs.
A Monte Carlo simulation can then be run using these hopping rates.
Because this is a quantum chemical calculation, the position of each atom is needed--therefore a backmapping process is required to calculate the charge transport in a CG morphology.
MorphCT has some builtin backmapping tools which use xml file (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...

\section*{Preliminary Work}
<how do I relate this to what I want to do??>
- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
using these tools will help me to me a more efficient developer.
It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need further testing as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer.
This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
<atom typing is a pain and doing it manually is bad cite foyer paper>

@@

\section*{Research Plan}
- I will build on existing tools (signac,freud,mbuild,foyer,tim moore's msibi)
- create signac workflow which takes equilibrated atomistic trajectory (maybe checks if it's equilibrated?) maps the CG beads to it, runs IBI, gets tabulated FF, creates larger CG sim, runs it, does backmapping, then could do: RDF, charge transport, diffraction...
if this workflow is streamlined--it can be applied to many different compounds allowing for us to compare the analyses between our zoo of compounds.
- maybe the workflow could even involve getting the equilibrated trajectory (atomtyping/fill box/run) with the new hoomd 3 api we could even set decorrelation time as a stop trigger...

\subsection*{Objective 1: Develop a coarse graining workflow}
build on existing tools (mbuild, openbabel, tim moores MSIBI code, hoomd, foyer?)
use SMARTS matching to specify mapping operators with relative ease
use MSIBI to parameterize forcefield parameters

\subsection*{Objective 2: Develop a backmapping workflow}
Given an equilibrated CG morphology, retrieve the atomistic one by mapping the SMARTS structures onto the position of the CG beads and then relaxing them with some position restraint.

\subsection*{Objective 3: Run CG simulation sweep of non-fullerene acceptor blends}
use signac to organize data
I think there are not great CG models for these compounds (ITIC PTB7) I found this paper \cite{Meng2019} that claims to do CGMD with PTB7 ITIC but the details are hidden in the SI and seem fishy. seems like they use IBI but they dont say how they got their target distributions.
can easily test out different mappings and "processing" conditions

\subsection*{Objective 4: Analysis}
Use charge transfer, diffraction to tell which models are the best
<cite a bunch of experimental papers we can compare to>
<cite our papers that show we can do this comparison already>
Our morphct paper says the mobilities we predict are 2x higher than experiment? why?

@@

\section*{Predicted Outcomes}
- understanding coarse graining (i'm stealing this from mike because I like it) how coarse is too coarse? for these new systems what is the minimal model which can reproduce the structural features
- understanding the interactions which guide BHJ self assembly. understanding which functionalizations/processing conditions make best morphology
- are smarts strings viable for use as mappings? where does using smarts strings break down?
- does making science easier/more understandable make it better?

\section*{Contingency Analysis}
<what's going to be hard?>

>>>>

\section*{Research Objectives}

<gain insight into the limits of coarse graining>
<create models for new opv compounds>
<create a workflow that will make creating new models more accessible>
<develop new tools that help humans do science>
<use that science to help solve energy crisis???????>
<I don't know where to put this but I want a section on best practices>
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
live coding, interactive \cite{Wilson2016}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}

@@

\subsection*{Organic Photovoltaics}

<what is PCE>
The power conversion efficiency (PCE or sometimes $\eta_{e}$) is the ratio of electrical power produced by the device over the power of incedent photons.
Higher PCE means the device is more efficient.  
The material properties which determine the PCE of a device are those which affect the number of photons absorbed, excitons dissociated, and free charges that reach the electrode.
The absorption efficiency depends on the absorption spectrum, absorption coefficient, and layer thickness.
The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface.
Finally, the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the electrons and holes.\cite{Hoppe2004}
<is there a citation for why charge transport is a good proxy for PCE?>

@@

\subsection*{Mesoscale Device Simulation}

<I DONT WANT TO FOCUS ON THIS TOO MUCH. It's only here as a rationale for why backmapping>
<how morphct pipeline would work: cg-backmap-ct>
MorphCT, a software previously developed by our lab, can simulate charge transport through an OPV morphology using kinetic Monte Carlo\cite{Miller2018a,MorphCT,morphct2.2}.
The kinetic Monte Carlo algorithm used by MorphCT uses the semi-empirical Zerner's Intermediate Neglect of Differential Overlap (ZINDO/S) quantum chemical calculation to obtain the molecular energy levels of chromophores in the morphology.
The HOMO levels of each chromophore site and the energy splitting induced in the chromophore pairs is used in the Marcus equation to calculate the charge hopping rate between pairs.
A Monte Carlo simulation can then be run using these hopping rates.
Because this is a quantum chemical calculation, the position of each atom is needed--therefore a backmapping process is required to calculate the charge transport in a CG morphology.
MorphCT has some builtin backmapping tools which use xml file (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
<making morphct more modular to allow it to be used in a workflow not cli>

\section*{Preliminary Work}

<how do I relate this to what I want to do??>
- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
using these tools will help me to me a more efficient developer.
It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need further testing as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer.
This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
<atom typing is a pain and doing it manually is bad cite foyer paper>

@@

\section*{Research Plan}

- I will build on existing tools (signac,freud,mbuild,foyer,tim moore's msibi)
- create signac workflow which takes equilibrated atomistic trajectory (maybe checks if it's equilibrated?) maps the CG beads to it, runs IBI, gets tabulated FF, creates larger CG sim, runs it, does backmapping, then could do: RDF, charge transport, diffraction...
if this workflow is streamlined--it can be applied to many different compounds allowing for us to compare the analyses between our zoo of compounds.
- maybe the workflow could even involve getting the equilibrated trajectory (atomtyping/fill box/run) with the new hoomd 3 api we could even set decorrelation time as a stop trigger...

\subsection*{Objective 1: Develop a coarse graining workflow}

build on existing tools (mbuild, openbabel, tim moores MSIBI code, hoomd, foyer?)
use SMARTS matching to specify mapping operators with relative ease
use MSIBI to parameterize forcefield parameters

\subsection*{Objective 2: Develop a backmapping workflow}

Given an equilibrated CG morphology, retrieve the atomistic one by mapping the SMARTS structures onto the position of the CG beads and then relaxing them with some position restraint.

\subsection*{Objective 3: Run CG simulation sweep of non-fullerene acceptor blends}

use signac to organize data
I think there are not great CG models for these compounds (ITIC PTB7) I found this paper \cite{Meng2019} that claims to do CGMD with PTB7 ITIC but the details are hidden in the SI and seem fishy. seems like they use IBI but they dont say how they got their target distributions.
can easily test out different mappings and "processing" conditions

\subsection*{Objective 4: Analysis}

Use charge transfer, diffraction to tell which models are the best
<cite a bunch of experimental papers we can compare to>
<cite our papers that show we can do this comparison already>
Our morphct paper says the mobilities we predict are 2x higher than experiment? why?

@@

\section*{Predicted Outcomes}

- understanding coarse graining (i'm stealing this from mike because I like it) how coarse is too coarse? for these new systems what is the minimal model which can reproduce the structural features
- understanding the interactions which guide BHJ self assembly. understanding which functionalizations/processing conditions make best morphology
- are smarts strings viable for use as mappings? where does using smarts strings break down?
- does making science easier/more understandable make it better?

\section*{Contingency Analysis}

<what's going to be hard?> 
maybe SMARTS SMILES won't work without careful choice of beads. This is a little annoying but still preferrable I think because at least the reasons may be understandable (the order of the beads matters) or chemically sensible (one SMILES string may contain another -- just as one chemical moeity may be composed of more submoeities <this is a word?>)
